Dynein walks like an Imperial AT-ST

### 2018-10-03 papers/paper/paper.tex
change figures and start converting to fac

\usepackage{subcaption}
\usepackage{breqn}

@@

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
  \includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
\caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
\label{fig:}
\end{figure}

>>>>

\usepackage{subcaption}
\usepackage{breqn}
\usepackage{color}

\newcommand\davidsays[1]{{\em\color{blue} {\bf DR:} #1}}

@@

\begin{figure}[tbhp]
  \centering
  a)\includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
  b)\includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
  c)\includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
\caption{\davidsays{Look up Yildiz figure for (a)}\textbf{Does our model capture dynamics a markov model wouldn't?}}
\label{fig:}
\end{figure}
